FAIR theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2025-02-19 manuscript.Rmd
Rephrase reference to paradigms

Successful communication requires shared background knowledge between sender and receiver [@vogtFAIR20Extending2024].
The Kuhnian notion of "normal science", conducted within the context of a shared paradigm, provides shared background knowledge to facilitate mutual understanding [@kuhnStructureScientificRevolutions2009].
From a pragmatic perspective, these considerations indicate that,
when striving to make theory accessible, 
it is important to be as explicit as possible (e.g., about assumptions  and ontological definitions), 
while acknowledging that accessibility exists on a spectrum, 
and that it is impossible to eliminate all ambiguity.
Rather, it may benefit scientific discourse to anticipate misunderstanding,
and use it to drive further explication of theory.
In sum, efforts to communicate theory clearly, with as few dependencies on shared background knowledge as possible, including by formalization, explication of assumptions,
and cross-references to resources that provide relevant context (papers, ontologies, macro-theories, theories of measurement)
will advance its Accessibility [@langeChecklist2025].

>>>>

Successful communication requires shared background knowledge between sender and receiver [@vogtFAIR20Extending2024].
The notion of "normal science" describes a phase in which a scientific community operates within the context of a shared paradigm,
creating the background knowledge needed for mutual understanding and productive scientific work [@kuhnStructureScientificRevolutions2009].
In reality, however, paradigms are rarely clear-cut, and shared background knowledge can come from different sources, or be problematically absent.
From a pragmatic perspective,
this underscores the importance of being as explicit as possible about assumptions and ontological definitions when making theory Accessible,
while acknowledging that Accessibility exists on a spectrum, 
and that it is impossible to eliminate all ambiguity.
Rather, it may benefit scientific discourse to anticipate misunderstanding,
and use it to drive further explication of theory.
In sum, efforts to communicate theory clearly, with as few dependencies on shared background knowledge as possible, including by formalization, explication of assumptions,
and cross-references to resources that provide relevant context (papers, ontologies, macro-theories, theories of measurement)
will advance its Accessibility [@langeChecklist2025].
